---
title: "To use lrem package"
author: "Zipson XU"
date: '`r format(Sys.time(), "%d, %m, %Y")`'
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Vignette Title}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}

---
This package is solving linear rational expectation models, using the function "lre_auto", which contains two functions: lre_auto_bk, introduced by Blanchard and Kahn(1980), and lre_auto_klein, introduced by Klein(2000).

## Examples

```{r, cache = FALSE, include = FALSE}
source("F:/ecomovement/lrem/R/lrem.R")
```

1, For the Blanchard and Kahn(1980) system as following:
$$
x_{t+1} = Ax_t
\Leftrightarrow
\begin{bmatrix}
  x_{t+1}^1 \\
  x_{t+1}^2
\end{bmatrix}
=
\begin{bmatrix}
  A_{11} & A_{12} \\
  A_{21} & A_{22}
\end{bmatrix}
\begin{bmatrix}
  x_{t}^1 \\
  x_{t}^2
\end{bmatrix},
$$
We can define:
```{r, }
A <- matrix(c( 0.7000000, 0.000000, 1.2000000, 0.6363636, 1.909091, 0.1818182, 0.0000000, -1.000000, 1.0000000 ), byrow = TRUE, nrow = 3)
x0 <- 0.1
```
As there is no E in this system, we can use the function as following:
```{r, }
lre_auto (A, ,x0)
```
Then we define g and h as following, accroding to the system:
\begin{align}
  x_t^2 &= g(x_t^1) \\
  x_{t+1}^1 &= h(x_t^1, x_t^2) = h(x_t). 
\end{align}

Therefore
```{r, }
g <- lre_auto (A, ,x0)$g
h <- lre_auto (A, ,x0)$h
```
and we set t=100
```{r, }
t <- 100
```

Here we can do the simulation:
```{r,}
simulate <- function(g, h, x0, t) {
n1 <- length(x0)  
n2 <- length(g(x0)) 
pre <- 1:n1 
npr <- (n1 + 1):(n1 + n2)
out <- matrix(0, t, n1 + n2)
out[1, pre] <- x0  
out[1, npr] <- g(x0) 
for (i in 1:(t - 1)) 
{ out[i + 1, pre] <- h(out[i, pre]) 
out[i + 1, npr] <- g(out[i + 1, pre]) } 
out
}

simulate(g, h, x0, t)
out<-simulate(g, h, x0, t)
plot(out[, 1])
```

2, For the Klein(2000) case:
We use the matrix A and B in "http://www.nag.com/lapack-ex/node119.html" as A and E

```{r,}
A <- QZ::exAB2$A
E <- QZ::exAB2$B
ret <- QZ::qz(A, E)
abs(ret$ALPHA / ret$BETA)
ord <- abs(ret$ALPHA / ret$BETA) <= 1
ret2 <- QZ::qz.dtgsen(ret$S, ret$T, ret$Q, ret$Z, select = ord)
abs(ret2$ALPHA / ret2$BETA)
```

Therefore, we define
```{r, }
g <- lre_auto (A,E,x0)$g
h <- lre_auto (A,E,x0)$h
```

Then the simulation result becoms:
```{r,}
simulate <- function(g, h, x0, t) {
n1 <- length(x0)  
n2 <- length(g(x0)) 
pre <- 1:n1 
npr <- (n1 + 1):(n1 + n2)
out <- matrix(0, t, n1 + n2)
out[1, pre] <- x0  
out[1, npr] <- g(x0) 
for (i in 1:(t - 1)) 
{ out[i + 1, pre] <- h(out[i, pre]) 
out[i + 1, npr] <- g(out[i + 1, pre]) } 
out
}

simulate(g, h, x0, t)
out<-simulate(g, h, x0, t)
plot(out[, 1])
```
